Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-05-31 writeup/gz_hubble_data.tex
Text is now Britishised.

\begin{abstract}
We present the data release paper for the Galaxy Zoo: Hubble (GZH)
project.\footnote{This publication has been made possible by the participation
of more than 200,000~volunteers in the Galaxy Zoo project. Their contributions
are individually acknowledged at
\url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a
large effort to measure reliable, detailed morphologies of galaxies by using
crowdsourced visual classifications of color composite images. Images in GZH
were selected from various publicly-released \textit{Hubble Space Telescope}
Legacy programs conducted with the Advanced Camera for Surveys, with filters that probe
the rest-frame optical emission from galaxies out to $z\sim1$.  The bulk of the
sample is selected to have $m_{I814W}<23.5$, but goes as faint as
$m_{I814W}<26.8$ for deep images combined over 5~epochs. The median redshift of
the combined samples is $\langle z\rangle=0.9\pm0.6$, with a tail extending out
to $z\simeq4$. The GZH morphological data include measurements of both bulge-
and disk-dominated galaxies, details on spiral disk structure that relate to
the Hubble type, bar identification, and numerous measurements of clump
identification and geometry.  This paper also describes a new method for
calibrating morphologies for galaxies of different luminosities and at
different redshifts by using artificially-redshifted galaxy images as a
baseline. The GZH catalog contains both raw and calibrated morphological vote
fractions for $119,849$~galaxies, providing the largest dataset to date
suitable for large-scale studies of galaxy evolution out to $z\sim1$. 
% Number = hubble + goods_shallow + stripe82_coadd
\end{abstract}

\begin{keywords}
galaxies:structure --- galaxies:high redshift --- galaxies:evolution
--- methods:data analysis --- catalogs
\end{keywords}

@@

Observational studies of galaxies at high-redshift also display a wide range of
morphological types, many of which are rare or absent at $z\sim0$.  These
include spheroids and disks (akin to the ellipticals and spirals seen in the
local Universe), but also a significant population of massive, more irregular
galaxies, including mergers, tadpoles, chains, double-clumps, and
clump-clusters \citep{elm05,elm07,cam11a,for11a,kar15}.  In contrast, while
grand-design spirals have been observed as far back as $z=2.18$ \citep{law12},
their spatial density suggests that they are exceedingly rare at these high
redshifts, with a very low overall disk fraction \citep{mor13}. Current
observational data thus strongly suggests that the classical Hubble
sequence/tuning fork \citep{hub36} is not a suitable framework for
characterizing high-redshift morphology.

Space-based observatories, particularly the \hubble{} (\hst), have been
responsible for the bulk of imaging studies of high-redshift galaxies.
Observations of fields with very deep imaging
\citep[eg,][]{wil96,gia04,bec06,dav07,sco07,gro11} give the photometric
sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also
providing the angular resolution to distinguish internal structure and
characterize the morphology. While these measurements are helped by the fact
that the angular diameter distance is relatively flat beyond $z>1$ in a flat
$\Lambda$CDM cosmology, the relevant angular scales are only of the order
$\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}. \hst{} can thus resolve
much of the structure for a Milky Way-sized galaxy out to moderately high
redshifts (at least distinguishing a disk from a bulge), but is limited for
more compact structures. Since the size of galaxies evolves as roughly
$r\propto(1+z)^{-1}$ \citep{mao98,law12a}, the compact sizes of high-redshift
galaxies make detailed morphologies a challenge even for \hst{} \citep{che12}.
However, the public availability of more than $10^5$~galaxies in archival
imaging has generated a sample with the potential
for statistically-robust studies of galaxy demographics and evolution.

One of the major difficulties in studying the morphologies of galaxies lies in
the techniques used for measurement. Visual classification by experts has been
used for many decades \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}.
These methods have the advantage of using the significant processing power of
the human brain to identify patterns, but suffer from issues such as lack of
scaling to large surveys and potential issues with replicability and
calibration (e.g., see \citealt{lah95} for a discussion on the extent to which
eight expert classifiers agree with each other). Automated measurements, both
parametric \citep{pen02a,sim11,lac12} and non-parametric
\citep{abr03,con03,lot04,sca07,bam08,fre13}, scale well to very large sample
sizes, but do not always fully capture the relevant features, especially for
asymmetric galaxies that become increasingly common at high redshifts. The
Galaxy Zoo project \citep{lin08,for12} utilizes crowdsourced visual classifications
to measure galaxies in color-composite images. The efforts of more than
$2\times10^5$~classifiers allow for multiple independent classifications of
each image which are combined and calibrated to give a distribution of vote
fractions proportional to the probability of a feature being visible. While
crowdsourced data require extensive calibration \citep{bam09,wil13}, they have
a proven reliability and have been used for a wide variety of scientific
studies \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.

@@

The sample selection and creation of the images used for GZH is described in
Section~\ref{sec:data}. Section~\ref{sec:interface} describes the GZH interface
and the collection of classifications. Section~\ref{sec:debiasing} outlines the
process used to calibrate and correct the crowdsourced vote fractions for
redshift-dependent bias. Section~\ref{sec:results} gives the main catalog of
results, with several examples of how the data may be queried in
Section~\ref{sec:cookbook}. Section~\ref{sec:analysis} gives a short overview
of the observed morphological demographics and compares them to several other
catalogs, with a summary in Section~\ref{sec:summary}.

@@

\begin{figure*}
\includegraphics[width=160mm]{figures/filter_curves.pdf}
\caption{Transmission curves of the filters used by \hst{} Advanced Camera for
Surveys (ACS) in wide-field channel mode for the various surveys in GZH. The
unfilled black curves show the filters for the Suprime Camera on \subaru, which
was used to create color gradients in the GZH COSMOS
images.}
\label{fig:filtercurves}
\end{figure*}

@@

\item The All-Wavelength Extended Groth Strip International Survey
    \citep[AEGIS;][]{dav07} covers a strip centered at
    $\alpha=14^\textrm{h}17^\textrm{m}, \delta=+52^\circ30^\prime$. This area
    of the sky was selected for a deep survey due to a combination of low
    extinction and low Galactic/zodiacal emission. The ACS images covered 63
    separate tiles over a total area of $\sim710$~arcmin$^2$. The two ACS bands
    for AEGIS had exposure times of 2300~seconds in F606W (\Vband) and
    2100~seconds in F814W (\Iband). The final mosaic images were dithered
    to a resolution of 0.03~\arcsec/pixel. For extended objects, the
    limiting magnitude of sources was 26.23~(AB) in \Vband{} and 25.61 (AB) in
    \Iband.

@@

\item The Galaxy Evolution from Morphologies and SEDs
    \citep[GEMS;][]{rix04,cal08} survey was centered on the Chandra Deep
    Field-South. The GEMS data covered $\sim800$~arcmin$^2$, completely surrounding
    the area covered by GOODS-S. Images from ACS in GEMS had 1~orbit per pointing
    for a total of 63~pointings. The exposure times were 2160 and 2286~seconds in
    \Vband{} and \zband{}, respectively. The image resolution had a pixel scale
    of 0.03~\arcsec/pixel. The $5\sigma$ limiting magnitude for source
    detection was 25.7~AB in \Vband{} and 24.2~AB in \zband.

\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covered an area of
    $\sim1.8$~deg$^2$ centered at $\alpha=10^\textrm{h}00^\textrm{m},
    \delta=+02^\circ12^\prime$. Its location near the celestial equator was
    designed to enable coverage by ground-based telescopes in both the Northern and
    Southern Hemispheres, in addition to space-based observatories. The ACS data
    for COSMOS consisted of 1~orbit per pointing with an exposure time of
    2028~seconds in \Iband; 590~total pointings were used to cover the entire
    field. The image resolution was dithered to 0.05~\arcsec/pixel. The 50\%
    completeness magnitude for a galaxy with a half-light radius of
    $0.50^{\prime\prime}$ in \Iband{} was 24.7~mag.

@@

Images from \hst{} legacy surveys were used to create multiple different color
and grayscale images using different depths and filter combinations; these are
described further in Section \ref{ssec:images}. Additionally, the use of a
small set of \hst{} images to create simulated images of active galactic
nucleus (AGN) host galaxies is described in Section \ref{ssec:sim_agn}.

@@

As active galactic nuclei often have bright, unresolved optical emission, AGN
have the potential to mimic or distort the identification of a bulge component.
GZH thus includes a set of images designed to measure the effect of AGN on
morphological classifications.  The presence of an AGN was simulated by
modeling the point spread function (PSF) of the telescope and then inserting a
bright source near the center of a real galaxy. For each image, the simulated
AGN was assigned one of three colors -- either blue, red, or flat (white) as
seen in the color images -- and a range of brightnesses such that
$L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in
$(0.2,1.0,5.0,10.0,50.0)$. Combining these parameters generated 15~images
with different simulated AGN for each host, in addition to the original galaxy
image.

@@

%The selection criteria for the different morphological categories is
%summarized in Table \ref{tbl:morphologies}.

@@

In addition to the physical parameters of the input images, the \ferengi{}
output depends on assumptions of the global galaxy evolution model.
This evolution is parameterized by a crude model that mimics the brightness increase of galaxies
with increasing redshift \citep[\eg,][]{lil98,lov12}. The effect on the
redshifted images is simply an empirical addition to the magnitude of a galaxy
of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and
$e$ is the evolutionary correction in magnitudes ($e=-1$ essentially
brightens the entire galaxy by 1~magnitude by $z=1$). \ferengi{} was run on the images
for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments
of $\Delta e = 0.5$. Figure~\ref{fig:exampleFERENGI} shows several examples
of the effects of ``losing'' spiral/disk features with increasing redshift
for two galaxies with no evolution corrections ($e=0$); as the signal-to-noise ratio in the images
decreases and the galaxies become fainter, the contrast between features
like spiral arms goes down and \ffeatures{} drops to the point where both
galaxies would have been classified as likely ellipticals.

@@

\subsection{Creating color images}\label{ssec:images}

The images used for classification in GZH were color-composite JPEGs made from
multi-band data. These were created following the method of \citet{lup04}, which
preserves color information irrespective of intensity.  An asinh intensity
mapping was applied to enhance the appearance of faint features while avoiding
saturating galaxy centers. The relative scalings of the filter bands were
chosen while trying to reproduce the color appearance of the SDSS images in
previous iterations of Galaxy Zoo.

@@

The COSMOS survey provides only \Iband{} HST imaging. For these galaxies, GZH
used ``pseudocolor'' images created by using the ACS \Iband{} data as an
illumination map and ground-based imaging from the \subaru{} telescope in
$B_J$, $r^+$, and $i^+$ filters to provide color information (see
\citealt{gri12} for further details). This resulted in images with the angular
resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the overall intensity, but
color gradients at ground-based resolution, with seeing between 0.95\arcsec{}
and 1.05\arcsec{} \citep{tan07}.

Stripe~82 single-epoch images were taken directly from the DR7 SDSS SkyServer,
which combined $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the
RGB channels \citep{nie04}. The co-added Stripe~82 images were assembled from runs 106 and
206 in DR7 and processed into color composites in the same manner as previous
iterations of Galaxy~Zoo.

In some cases, we found that attempting to emphasize faint features in the
images resulted in the sky noise taking the appearance of brightly colored
speckles. This impaired the aesthetics of the images and might have been a
distraction to visual classification.  To counteract this, a soft-edged object
mask was applied to the color images and a desaturation operation performed.
This masking procedure was effective in preserving the color balance for
galaxies and retained the visibility of faint features, while reducing the color
contrast in the sky noise and greatly improving the appearance of the images.
This solution was applied to the coadded Stripe~82, COSMOS and 5-epoch GOODS
images.

In addition to the primary \hst{} legacy imaging sample with colored images
described as above, GZH also includes samples of \hst{} galaxy images with
different color prescriptions. In particular, there are two sets of 3,927~images
each, drawn from the COSMOS sample; the first has a dramatically reduced color
saturation, and the second has reversed the colors so that the blue and red
filters have exchanged places in the RGB image. The `faded' galaxy set
facilitates measuring of possible variations in classification due to the
presence or absence of color features. The `recolored' set enables an
alternative test of potential color biases in classifications.
% I guess this means we need to say somewhere later that we don't see an effect
% (we don't, right?).  Would also be good to cite here where we have done
% similar things in the past... - BDS

The simulated AGN host galaxy color images (described in Section \ref{ssec:sim_agn})
were created using the same prescription as for the GOODS 2-epoch imaging. The
artificially redshifted color images (Section \ref{ssec:ferengi}) were created using the
same prescription as for the AEGIS images.
% Edmond should verify the AEGIS bit above. - BDS

@@

The full GZH sample is composed of 8~different galaxy sub-samples. Throughout
this paper and in the published catalogs they are referred to with the
following labels:

@@

%\ref{tbl:catalog_hst}
\item \main: \hst{} imaging with RGB colors making use of all available
filters with typical saturation and in correct order, as described in
Section~\ref{ssec:images}. This sample includes AEGIS, COSMOS, GEMS, and
full-depth GOODS (North and South) images. (113,705~galaxies)

%\ref{tbl:catalog_faded}
\item \faded: a subset of COSMOS images with very low color saturation.
(3,927~galaxies)

@@

%\ref{tbl:catalog_goods_shallow}
\item \goods: Images from GOODS-North and GOODS-South, with
color from 2~filters and imaged at 2-epoch depth. (6,144~galaxies)

@@

Redshifts for the GZH catalog were compiled from a variety of sources. For each
galaxy, the primary redshift is in the $\tt Z\_BEST$ column of
Table~\ref{tbl:catalog_hst}. The redshift type (spectroscopic: $\tt SPEC\_Z$,
photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column
$\tt Z\_BEST\_TYPE$, and the source catalog of the redshift is included as $\tt
Z\_BEST\_SOURCE$.

For galaxies which have published redshifts from multiple sources, the
following algorithm was used to select the $\tt Z\_BEST$ quantity. A
high-quality spectroscopic redshift in the ACS-GC is the primary option,
provided in the ACS-GC \citep{gri12}, 3DHST \citep{mom15}, and MUSYC
\citep{car10} catalogs and used in that order. For galaxies with multiple
spectroscopic redshifts, more than 98\% are consistent ($\Delta z<0.001$), and
so the order of selection made no practical difference. Galaxies with
inconsistent spectroscopic redshifts between any pair of catalogs are marked
with a flag in Table~\ref{tbl:catalog_hst}.  If no spectroscopic redshifts were
available, the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST,
MUSYC, UltraVISTA;][]{ilb13} and UltraVISTA grism data were used. The
measurement with the smallest reported 1-$\sigma$ error was selected in each
case.
%Table~\ref{tbl:redshifts} shows the results of this selection.

%\begin{figure*}
%\center
%\includegraphics[width=160mm]{figures/specz_comparison.pdf}
%\caption{Spectroscopic redshifts from the ACS-GC, 3DHST, and MUSYC catalogs.
%The number in the upper left of each plot is the percentage of redshifts which
%agree within $\Delta z < 0.05$ between the two catalogs being compared in each
%panel. Within this range there is over 98\% agreement in redshifts between all
%three catalogs.}
%\label{fig:speczs}
%\end{figure*}

@@

Classifications for GZH were made using a web-based interface
(Figure~\ref{fig:interface}), similar in design to Galaxy~Zoo and Galaxy~Zoo~2.
The front-end runs on a Ruby~on~Rails framework with classifications stored in
a MySQL backend. Classifiers were shown a randomly-selected color composite image from
the GZH sample; the default showed the image with a black sky background,
although they had the option to invert the color palette if desired. The
questions and responses for morphology appeared on the right side of the image as
a panel, including both text and icons. There was no tutorial required for
participation, although classifiers could access an extensive ``Help'' section
containing example images and descriptive text for all the morphological
labels.

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/gzh_decision_tree.pdf}
\caption{Flowchart of the questions presented to GZH classifiers, labeled with
the corresponding task numbers. Tasks in the decision tree are color-coded by
tier level: Gray-colored tasks are 1$^\mathrm{st}$-tier questions which are
asked in every classification. Tasks colored green, blue, purple, and pink
(respectively) are one, two, three, or four steps below branching points in the
decision tree. The dashed line between T15 and T03 indicates the unique case
where volunteers could label both clumpy and disk-like morphologies for
galaxies with clumps arranged in a spiral pattern.}
\label{fig:decisiontree}
\end{figure*}

The procedure for classifying an image in GZH followed a hierarchical decision
tree (Figure~\ref{fig:decisiontree}). Every classification began with the step of
identifying whether the object at the center of the image was a smooth galaxy,
a galaxy with a disk or other features, or a star/artifact. Subsequent
questions in the tree depended on the previous answer(s) given by the classifier; the
decision tree was designed so that every question relevant to
the morphology in the process of being identified was answered. Questions that were not
answered were implicitly assumed to be absent in the image --- for example, if
the classifier identified a galaxy as being smooth, they were not asked to count the
number of spiral arms. For every task, the classifier chose a single answer before
continuing to the next question; they also had the option to restart any
classification in-progress.

@@

\section{Using the catalog}\label{sec:cookbook}

>>>>

\begin{abstract}
We present the data release paper for the Galaxy Zoo: Hubble (GZH)
project.\footnote{This publication has been made possible by the participation
of more than 200,000~volunteers in the Galaxy Zoo project. Their contributions
are individually acknowledged at
\url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a
large effort to measure reliable, detailed morphologies of galaxies by using
crowdsourced visual classifications of colour composite images. Images in GZH
were selected from various publicly-released \textit{Hubble Space Telescope}
Legacy programs conducted with the Advanced Camera for Surveys, with filters that probe
the rest-frame optical emission from galaxies out to $z\sim1$.  The bulk of the
sample is selected to have $m_{I814W}<23.5$, but goes as faint as
$m_{I814W}<26.8$ for deep images combined over 5~epochs. The median redshift of
the combined samples is $\langle z\rangle=0.9\pm0.6$, with a tail extending out
to $z\simeq4$. The GZH morphological data include measurements of both bulge-
and disk-dominated galaxies, details on spiral disk structure that relate to
the Hubble type, bar identification, and numerous measurements of clump
identification and geometry.  This paper also describes a new method for
calibrating morphologies for galaxies of different luminosities and at
different redshifts by using artificially-redshifted galaxy images as a
baseline. The GZH catalogue contains both raw and calibrated morphological vote
fractions for $119,849$~galaxies, providing the largest dataset to date
suitable for large-scale studies of galaxy evolution out to $z\sim1$. 
% Number = hubble + goods_shallow + stripe82_coadd
\end{abstract}

\begin{keywords}
galaxies:structure --- galaxies:high redshift --- galaxies:evolution
--- methods:data analysis --- catalogues
\end{keywords}

@@

Observational studies of galaxies at high-redshift also display a wide range of
morphological types, many of which are rare or absent at $z\sim0$.  These
include spheroids and disks (akin to the ellipticals and spirals seen in the
local Universe), but also a significant population of massive, more irregular
galaxies, including mergers, tadpoles, chains, double-clumps, and
clump-clusters \citep{elm05,elm07,cam11a,for11a,kar15}.  In contrast, while
grand-design spirals have been observed as far back as $z=2.18$ \citep{law12},
their spatial density suggests that they are exceedingly rare at these high
redshifts, with a very low overall disk fraction \citep{mor13}. Current
observational data thus strongly suggests that the classical Hubble
sequence/tuning fork \citep{hub36} is not a suitable framework for
characterising high-redshift morphology.

Space-based observatories, particularly the \hubble{} (\hst), have been
responsible for the bulk of imaging studies of high-redshift galaxies.
Observations of fields with very deep imaging
\citep[eg,][]{wil96,gia04,bec06,dav07,sco07,gro11} give the photometric
sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also
providing the angular resolution to distinguish internal structure and
characterise the morphology. While these measurements are helped by the fact
that the angular diameter distance is relatively flat beyond $z>1$ in a flat
$\Lambda$CDM cosmology, the relevant angular scales are only of the order
$\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}. \hst{} can thus resolve
much of the structure for a Milky Way-sized galaxy out to moderately high
redshifts (at least distinguishing a disk from a bulge), but is limited for
more compact structures. Since the size of galaxies evolves as roughly
$r\propto(1+z)^{-1}$ \citep{mao98,law12a}, the compact sizes of high-redshift
galaxies make detailed morphologies a challenge even for \hst{} \citep{che12}.
However, the public availability of more than $10^5$~galaxies in archival
imaging has generated a sample with the potential
for statistically-robust studies of galaxy demographics and evolution.

One of the major difficulties in studying the morphologies of galaxies lies in
the techniques used for measurement. Visual classification by experts has been
used for many decades \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}.
These methods have the advantage of using the significant processing power of
the human brain to identify patterns, but suffer from issues such as lack of
scaling to large surveys and potential issues with replicability and
calibration (e.g., see \citealt{lah95} for a discussion on the extent to which
eight expert classifiers agree with each other). Automated measurements, both
parametric \citep{pen02a,sim11,lac12} and non-parametric
\citep{abr03,con03,lot04,sca07,bam08,fre13}, scale well to very large sample
sizes, but do not always fully capture the relevant features, especially for
asymmetric galaxies that become increasingly common at high redshifts. The
Galaxy Zoo project \citep{lin08,for12} utilises crowdsourced visual classifications
to measure galaxies in colour-composite images. The efforts of more than
$2\times10^5$~classifiers allow for multiple independent classifications of
each image which are combined and calibrated to give a distribution of vote
fractions proportional to the probability of a feature being visible. While
crowdsourced data require extensive calibration \citep{bam09,wil13}, they have
a proven reliability and have been used for a wide variety of scientific
studies \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.

@@

The sample selection and creation of the images used for GZH is described in
Section~\ref{sec:data}. Section~\ref{sec:interface} describes the GZH interface
and the collection of classifications. Section~\ref{sec:debiasing} outlines the
process used to calibrate and correct the crowdsourced vote fractions for
redshift-dependent bias. Section~\ref{sec:results} gives the main catalogue of
results, with several examples of how the data may be queried in
Section~\ref{sec:cookbook}. Section~\ref{sec:analysis} gives a short overview
of the observed morphological demographics and compares them to several other
catalogues, with a summary in Section~\ref{sec:summary}.

@@

\begin{figure*}
\includegraphics[width=160mm]{figures/filter_curves.pdf}
\caption{Transmission curves of the filters used by \hst{} Advanced Camera for
Surveys (ACS) in wide-field channel mode for the various surveys in GZH. The
unfilled black curves show the filters for the Suprime Camera on \subaru, which
was used to create colour gradients in the GZH COSMOS
images.}
\label{fig:filtercurves}
\end{figure*}

@@

\item The All-Wavelength Extended Groth Strip International Survey
    \citep[AEGIS;][]{dav07} covers a strip centred at
    $\alpha=14^\textrm{h}17^\textrm{m}, \delta=+52^\circ30^\prime$. This area
    of the sky was selected for a deep survey due to a combination of low
    extinction and low Galactic/zodiacal emission. The ACS images covered 63
    separate tiles over a total area of $\sim710$~arcmin$^2$. The two ACS bands
    for AEGIS had exposure times of 2300~seconds in F606W (\Vband) and
    2100~seconds in F814W (\Iband). The final mosaic images were dithered
    to a resolution of 0.03~\arcsec/pixel. For extended objects, the
    limiting magnitude of sources was 26.23~(AB) in \Vband{} and 25.61 (AB) in
    \Iband.

@@

\item The Galaxy Evolution from Morphologies and SEDs
    \citep[GEMS;][]{rix04,cal08} survey was centred on the Chandra Deep
    Field-South. The GEMS data covered $\sim800$~arcmin$^2$, completely surrounding
    the area covered by GOODS-S. Images from ACS in GEMS had 1~orbit per pointing
    for a total of 63~pointings. The exposure times were 2160 and 2286~seconds in
    \Vband{} and \zband{}, respectively. The image resolution had a pixel scale
    of 0.03~\arcsec/pixel. The $5\sigma$ limiting magnitude for source
    detection was 25.7~AB in \Vband{} and 24.2~AB in \zband.

\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covered an area of
    $\sim1.8$~deg$^2$ centred at $\alpha=10^\textrm{h}00^\textrm{m},
    \delta=+02^\circ12^\prime$. Its location near the celestial equator was
    designed to enable coverage by ground-based telescopes in both the Northern and
    Southern Hemispheres, in addition to space-based observatories. The ACS data
    for COSMOS consisted of 1~orbit per pointing with an exposure time of
    2028~seconds in \Iband; 590~total pointings were used to cover the entire
    field. The image resolution was dithered to 0.05~\arcsec/pixel. The 50\%
    completeness magnitude for a galaxy with a half-light radius of
    $0.50^{\prime\prime}$ in \Iband{} was 24.7~mag.

@@

Images from \hst{} legacy surveys were used to create multiple different colour
and greyscale images using different depths and filter combinations; these are
described further in Section \ref{ssec:images}. Additionally, the use of a
small set of \hst{} images to create simulated images of active galactic
nucleus (AGN) host galaxies is described in Section \ref{ssec:sim_agn}.

@@

As active galactic nuclei often have bright, unresolved optical emission, AGN
have the potential to mimic or distort the identification of a bulge component.
GZH thus includes a set of images designed to measure the effect of AGN on
morphological classifications.  The presence of an AGN was simulated by
modelling the point spread function (PSF) of the telescope and then inserting a
bright source near the centre of a real galaxy. For each image, the simulated
AGN was assigned one of three colours -- either blue, red, or flat (white) as
seen in the colour images -- and a range of brightnesses such that
$L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in
$(0.2,1.0,5.0,10.0,50.0)$. Combining these parameters generated 15~images
with different simulated AGN for each host, in addition to the original galaxy
image.

@@

%The selection criteria for the different morphological categories is
%summarised in Table \ref{tbl:morphologies}.

@@

In addition to the physical parameters of the input images, the \ferengi{}
output depends on assumptions of the global galaxy evolution model.
This evolution is parameterised by a crude model that mimics the brightness increase of galaxies
with increasing redshift \citep[\eg,][]{lil98,lov12}. The effect on the
redshifted images is simply an empirical addition to the magnitude of a galaxy
of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and
$e$ is the evolutionary correction in magnitudes ($e=-1$ essentially
brightens the entire galaxy by 1~magnitude by $z=1$). \ferengi{} was run on the images
for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments
of $\Delta e = 0.5$. Figure~\ref{fig:exampleFERENGI} shows several examples
of the effects of ``losing'' spiral/disk features with increasing redshift
for two galaxies with no evolution corrections ($e=0$); as the signal-to-noise ratio in the images
decreases and the galaxies become fainter, the contrast between features
like spiral arms goes down and \ffeatures{} drops to the point where both
galaxies would have been classified as likely ellipticals.

@@

\subsection{Creating colour images}\label{ssec:images}

The images used for classification in GZH were colour-composite JPEGs made from
multi-band data. These were created following the method of \citet{lup04}, which
preserves colour information irrespective of intensity.  An asinh intensity
mapping was applied to enhance the appearance of faint features while avoiding
saturating galaxy centres. The relative scalings of the filter bands were
chosen while trying to reproduce the colour appearance of the SDSS images in
previous iterations of Galaxy Zoo.

@@

The COSMOS survey provides only \Iband{} HST imaging. For these galaxies, GZH
used ``pseudocolour'' images created by using the ACS \Iband{} data as an
illumination map and ground-based imaging from the \subaru{} telescope in
$B_J$, $r^+$, and $i^+$ filters to provide colour information (see
\citealt{gri12} for further details). This resulted in images with the angular
resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the overall intensity, but
colour gradients at ground-based resolution, with seeing between 0.95\arcsec{}
and 1.05\arcsec{} \citep{tan07}.

Stripe~82 single-epoch images were taken directly from the DR7 SDSS SkyServer,
which combined $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the
RGB channels \citep{nie04}. The co-added Stripe~82 images were assembled from runs 106 and
206 in DR7 and processed into colour composites in the same manner as previous
iterations of Galaxy~Zoo.

In some cases, we found that attempting to emphasise faint features in the
images resulted in the sky noise taking the appearance of brightly-coloured
speckles. This impaired the aesthetics of the images and might have been a
distraction to visual classification.  To counteract this, a soft-edged object
mask was applied to the colour images and a desaturation operation performed.
This masking procedure was effective in preserving the colour balance for
galaxies and retained the visibility of faint features, while reducing the colour
contrast in the sky noise and greatly improving the appearance of the images.
This solution was applied to the coadded Stripe~82, COSMOS and 5-epoch GOODS
images.

In addition to the primary \hst{} legacy imaging sample with coloured images
described as above, GZH also includes samples of \hst{} galaxy images with
different colour prescriptions. In particular, there are two sets of 3,927~images
each, drawn from the COSMOS sample; the first has a dramatically reduced colour
saturation, and the second has reversed the colours so that the blue and red
filters have exchanged places in the RGB image. The `faded' galaxy set
facilitates measuring of possible variations in classification due to the
presence or absence of colour features. The `recoloured' set enables an
alternative test of potential colour biases in classifications.
% I guess this means we need to say somewhere later that we don't see an effect
% (we don't, right?).  Would also be good to cite here where we have done
% similar things in the past... - BDS

The simulated AGN host galaxy colour images (described in Section \ref{ssec:sim_agn})
were created using the same prescription as for the GOODS 2-epoch imaging. The
artificially redshifted colour images (Section \ref{ssec:ferengi}) were created using the
same prescription as for the AEGIS images.
% Edmond should verify the AEGIS bit above. - BDS

@@

The full GZH sample is composed of 8~different galaxy sub-samples. Throughout
this paper and in the published catalogues they are referred to with the
following labels:

@@

%\ref{tbl:catalog_hst}
\item \main: \hst{} imaging with RGB colours making use of all available
filters with typical saturation and in correct order, as described in
Section~\ref{ssec:images}. This sample includes AEGIS, COSMOS, GEMS, and
full-depth GOODS (North and South) images. (113,705~galaxies)

%\ref{tbl:catalog_faded}
\item \faded: a subset of COSMOS images with very low colour saturation.
(3,927~galaxies)

@@

%\ref{tbl:catalog_goods_shallow}
\item \goods: Images from GOODS-North and GOODS-South, with
colour from 2~filters and imaged at 2-epoch depth. (6,144~galaxies)

@@

Redshifts for the GZH catalogue were compiled from a variety of sources. For each
galaxy, the primary redshift is in the $\tt Z\_BEST$ column of
Table~\ref{tbl:catalogue_hst}. The redshift type (spectroscopic: $\tt SPEC\_Z$,
photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column
$\tt Z\_BEST\_TYPE$, and the source catalogue of the redshift is included as $\tt
Z\_BEST\_SOURCE$.

For galaxies which have published redshifts from multiple sources, the
following algorithm was used to select the $\tt Z\_BEST$ quantity. A
high-quality spectroscopic redshift in the ACS-GC is the primary option,
provided in the ACS-GC \citep{gri12}, 3DHST \citep{mom15}, and MUSYC
\citep{car10} catalogues and used in that order. For galaxies with multiple
spectroscopic redshifts, more than 98\% are consistent ($\Delta z<0.001$), and
so the order of selection made no practical difference. Galaxies with
inconsistent spectroscopic redshifts between any pair of catalogues are marked
with a flag in Table~\ref{tbl:catalogue_hst}.  If no spectroscopic redshifts were
available, the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST,
MUSYC, UltraVISTA;][]{ilb13} and UltraVISTA grism data were used. The
measurement with the smallest reported 1-$\sigma$ error was selected in each
case.
%Table~\ref{tbl:redshifts} shows the results of this selection.

%\begin{figure*}
%\center
%\includegraphics[width=160mm]{figures/specz_comparison.pdf}
%\caption{Spectroscopic redshifts from the ACS-GC, 3DHST, and MUSYC catalogues.
%The number in the upper left of each plot is the percentage of redshifts which
%agree within $\Delta z < 0.05$ between the two catalogues being compared in each
%panel. Within this range there is over 98\% agreement in redshifts between all
%three catalogues.}
%\label{fig:speczs}
%\end{figure*}

@@

Classifications for GZH were made using a web-based interface
(Figure~\ref{fig:interface}), similar in design to Galaxy~Zoo and Galaxy~Zoo~2.
The front-end runs on a Ruby~on~Rails framework with classifications stored in
a MySQL backend. Classifiers were shown a randomly-selected colour composite image from
the GZH sample; the default showed the image with a black sky background,
although they had the option to invert the colour palette if desired. The
questions and responses for morphology appeared on the right side of the image as
a panel, including both text and icons. There was no tutorial required for
participation, although classifiers could access an extensive ``Help'' section
containing example images and descriptive text for all the morphological
labels.

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/gzh_decision_tree.pdf}
\caption{Flowchart of the questions presented to GZH classifiers, labeled with
the corresponding task numbers. Tasks in the decision tree are colour-coded by
tier level: Grey-coloured tasks are 1$^\mathrm{st}$-tier questions which are
asked in every classification. Tasks coloured green, blue, purple, and pink
(respectively) are one, two, three, or four steps below branching points in the
decision tree. The dashed line between T15 and T03 indicates the unique case
where volunteers could label both clumpy and disk-like morphologies for
galaxies with clumps arranged in a spiral pattern.}
\label{fig:decisiontree}
\end{figure*}

The procedure for classifying an image in GZH followed a hierarchical decision
tree (Figure~\ref{fig:decisiontree}). Every classification began with the step of
identifying whether the object at the centre of the image was a smooth galaxy,
a galaxy with a disk or other features, or a star/artifact. Subsequent
questions in the tree depended on the previous answer(s) given by the classifier; the
decision tree was designed so that every question relevant to
the morphology in the process of being identified was answered. Questions that were not
answered were implicitly assumed to be absent in the image --- for example, if
the classifier identified a galaxy as being smooth, they were not asked to count the
number of spiral arms. For every task, the classifier chose a single answer before
continuing to the next question; they also had the option to restart any
classification in-progress.

@@

\section{Using the catalogue}\label{sec:cookbook}
